Cloud-SAP: Self-adaptive platform for scaling users' application deployed in a federation of cloud computing environments

### 2013-09-16 article/article.tex
Add the adaptability section to the article

\section{Adaptivity}
\section{Architecture of SAP-Cloud}

@@

% Non-BibTeX users please use
\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
\bibitem{NIST}
  {Mell, P. and Grance, T.}, {The NIST Definition of Cloud Computing}, 2011
\bibitem{InterCloud}
  {Buyya, R. Ranjan, R. and Calheiros, R.}, {InterCloud: Scaling of Applications across multiple Cloud Computing Environments}, 2010
\bibitem{MarketOriented}
  {Buyyaa, R., Yeoa, C., Venugopala, S., d Broberga, J. and Brandicc, I.}, {Cloud computing and emerging IT platforms: Vision, hype, and reality for delivering computing as the 5th utility}, {Future Generation Computer Systems}, vol.25, 2009
\bibitem{ScalingInDaCloud}
  {Vaquero, L., Rodero-Merino, L. and Buyya, R.}, {Dynamically Scaling Applications in the Cloud}, {ACM SIGCOMM Computer Communication Review}, vol.41, 2011
\bibitem{ScalabilityTerm}
  Bondi, A., {Characteristics of Scalability and Their Impact on Performance}, 2000
\bibitem{PharmaComputation}
  Jon Brodkin, \emph{\$1,279-per-hour, 30,000-core cluster built on Amazon EC2 cloud}, {\emph{Ars Technica}, \url{http://arstechnica.com/business/2011/09/30000-core-cluster-built-on-amazon-ec2-cloud/}}, last access: 16/09/2013
\bibitem{AWS}
  {Amazon Elastic Compute Cloud (EC2)}, {\url{http://aws.amazon.com/}}, last access: 16/09/2013 
\bibitem{GoogleAppEngine}
  {Google App Engine}, {\url{https://appengine.google.com/}}, last access: 16/09/2013 
\bibitem{Heroku}
  {Heroku}, {\url{https://www.heroku.com}}, last access: 16/09/2013 
\bibitem{Azure}
  {Windows Azure}, {\url{www.windowsazure.com/}}, last access: 16/09/2013 
% Format for Journal Reference
%Author, Article title, Journal, Volume, page numbers (year)
% Format for books
%Author, Book title, page numbers. Publisher, place (year)
% etc
\end{thebibliography}

>>>>

\section{Adaptivity}
Platform adaptivity adds auto-scaling features to a solution offered by a Platform-as-a-Service provider. The key concept is to have a Elasticity Controller which gathers probes from virtual machines and uses that knowledge to execute appropriate action on cloud instance, indirectly modifying consecutive probes \cite{VaRoBu11}.

\paragraph{Policies} Policy denotes a condition which, when satisfied, triggers an action that is supposed to harness cloud instance in a way that future evaluations of condition will be unsuccessful. Typically condition itself is accompanied by a minimal and maximal number of node instances, allowing for ensuring minimal QoS and controlling maximal costs. Currently, industry leaders supports two main kind of policies: \emph{expression based} and \emph{scheduled}. \emph{Expression-based} policy allows to define how to scale the application in response to changing conditions, which include factors such as memory, CPU usage, cost or some indirect, calculated metrics, while \emph{expression-based} scale the service according to load changes; for example, traffic increases during the weekends and decreases on working days. Hence, that predictable traffic patterns is used to scale application based on current time.

\paragraph{Data analysis}
Once the policies are defined, their conditions are evaluated against data acquired from sensors. In the simplest case this evaluation can be based on a Threshold Model \cite{LiWoZh05}, which defines a valid range. In cases when given metric violates that condition (i.e. value is either smaller than minimal or bigger than maximal acceptable) corresponding resource is properly adjusted.

\section{Architecture of SAP-Cloud}

@@

% Non-BibTeX users please use
\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
\bibitem{NIST}
  {Mell, P. and Grance, T.}, {The NIST Definition of Cloud Computing}, 2011
\bibitem{InterCloud}
  {Buyya, R. Ranjan, R. and Calheiros, R.}, {InterCloud: Scaling of Applications across multiple Cloud Computing Environments}, 2010
\bibitem{MarketOriented}
  {Buyyaa, R., Yeoa, C., Venugopala, S., d Broberga, J. and Brandicc, I.}, {Cloud computing and emerging IT platforms: Vision, hype, and reality for delivering computing as the 5th utility}, {Future Generation Computer Systems}, vol.25, 2009
\bibitem{ScalingInDaCloud}
  {Vaquero, L., Rodero-Merino, L. and Buyya, R.}, {Dynamically Scaling Applications in the Cloud}, {ACM SIGCOMM Computer Communication Review}, vol.41, 2011
\bibitem{ScalabilityTerm}
  Bondi, A., {Characteristics of Scalability and Their Impact on Performance}, 2000
\bibitem{PharmaComputation}
  Jon Brodkin, \emph{\$1,279-per-hour, 30,000-core cluster built on Amazon EC2 cloud}, {\emph{Ars Technica}, \url{http://arstechnica.com/business/2011/09/30000-core-cluster-built-on-amazon-ec2-cloud/}}, last access: 16/09/2013
\bibitem{AWS}
  {Amazon Elastic Compute Cloud (EC2)}, {\url{http://aws.amazon.com/}}, last access: 16/09/2013 
\bibitem{GoogleAppEngine}
  {Google App Engine}, {\url{https://appengine.google.com/}}, last access: 16/09/2013 
\bibitem{Heroku}
  {Heroku}, {\url{https://www.heroku.com}}, last access: 16/09/2013 
\bibitem{Azure}
  {Windows Azure}, {\url{www.windowsazure.com/}}, last access: 16/09/2013 
\bibitem{VaRoBu11}
  {Vaquero, L., Rodero-Merino, L. and Buyya, R.},{Dynamically Scaling Applications in the Cloud}, {ACM SIGCOMM Computer Communication Review}, vol.41, 2011
\bibitem{LiWoZh05}
 {Litoiu, M. and Woodside, M. and Zheng, T.}, {Hierarchical Model-based Autonomic Control of Software Systems}, {Design and evolution of autonomic application software}, 2005

% Format for Journal Reference
%Author, Article title, Journal, Volume, page numbers (year)
% Format for books
%Author, Book title, page numbers. Publisher, place (year)
% etc
\end{thebibliography}
